{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-28 paper/paper.tex
made references to typing rules universal

To define what noninterference means we need a notion of excution. It is assumed
that we have a sequential execution relation $\leadsto_{seq} \subseteq \text{SeqState} \times
\text{SeqState}$. The one step execution for the multithreaded language $\leadsto_{seq}
\subseteq (\text{ConcState} \times \text{History}) \times (\text{ConcState} \times \text{History})$ is defined
by the following rules.

@@

We now take a look at the rules of this type system concerning the \texttt{if} instruction.

>>>>

To define what noninterference means we need a notion of excution. It is assumed
that we have a sequential execution relation $\leadsto_{seq} \subseteq \text{SeqState} \times
\text{SeqState}$. The one step execution for the multithreaded language $\leadsto_{seq}
\subseteq (\text{ConcState} \times \text{History}) \times (\text{ConcState} \times \text{History})$ is defined
by the rules in figure \ref{fig:multithreaded-execution}.

@@

We now take a look at the rules of this type system concerning the \texttt{if} instruction, which are
defined in figure \ref{fig:typing-rules-if}.
